---
title: "tar2"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(dev = 'pdf')
require(xlsx)
require(psych)
require(plotrix)
require(plyr)
require(moments)                    # load e1071

```


#Part 1: 

```{r data, cache=TRUE, warning=FALSE, message=FALSE}
data <- read.xlsx("data_and_headers_processed.xlsx", 1, stringsAsFactors=T)
```

2. Possible problems:
  + Hebrew mixed with English - we took this problem and fixed the input file to include only english letters 
  + The sex feature have 2 missing values. You can see it here:
```{r, warning=FALSE, message=FALSE}
    summary(data$Sex)
```

  + The features don't really distribute noramly (i.e according to normal distribution) - it's not a problem by unless we assume it should distribute normaly. Here are few exmaples

```{r, warning=FALSE, message=FALSE}
    numeric.feature.names <- names(data)[c(which(names(data)=='QL1'):which(names(data)=='DI1'), which(names(data)=='BF2_Num'):which(names(data)=='S6'))]

    multi.hist(x = data[,numeric.feature.names[1:6]])

```

Create clarity, politeness, satisfaction variables
```{r warning=FALSE, message=FALSE}
data$Age <- as.numeric(as.character(data$Age))

data.for.clarity <- cbind(data[,c("C1", "C2", "C3", "C5")], 8-data$C4, 8-data$C6)
clarity <- apply(data.for.clarity, MARGIN = 1, FUN = mean)

data.for.politeness <- cbind(data[,c("P1", "P2", "P4", "P5", "P6")], 8-data$P3)
politeness <- apply(data.for.politeness, MARGIN = 1, FUN = mean)

data.for.satisfaction <- cbind(data[,c("S1", "S2", "S3", "S5", "S6")], 8-data$S4)
satisfaction <- apply(data.for.satisfaction, MARGIN = 1, FUN = mean)

#now adding them to the data frame
data <- cbind(data, clarity = clarity, politeness = politeness, satisfaction = satisfaction)
```



#Part 2
###Descriptive statistics (2.1)

```{r echo=FALSE, warning=FALSE, message=FALSE}

drawPieChart <- function (slices, lbls, main) {
  pct <- round(slices/sum(slices)*100)  #http://www.statmethods.net/graphs/pie.html
  lbls <- paste(lbls, pct) # add percents to labels 
  lbls <- paste(lbls,"%",sep="") # ad % to labels 
  pie3D(slices, labels = lbls, explode=0.1,main=main,labelcex =0.8)
  return()
}

drawHist <- function (histData, br, main) {
  hist(histData, col="red", breaks = br, main =main)
  return()
}


summaryDataFrame<- function(dataCol, dataColNames = NA) {
  dataColSummary <- summary(dataCol)
  resframe <- data.frame(matrix(unlist(dataColSummary), nrow=1, byrow=T))
  if (is.na(dataColNames)) {
    colnames(resframe) <- names(dataColSummary)
  }
  else if (length(colnames(resframe)) == length(dataColNames)){
    colnames(resframe) <- dataColNames
  }
  else {
    colnames(resframe) <- c(dataColNames, "NA's")
  }

  return(resframe)
}

combineSummaryFrame <- function (colData1, colData2, colnames=NA, rowNames) {
  combineFrame <- rbind.fill(summaryDataFrame(colData1, colnames), summaryDataFrame(colData2, colnames)) 
  rownames(combineFrame) <- rowNames
  return(combineFrame)
}


#http://myowelt.blogspot.co.il/2008/04/beautiful-correlation-tables-in-r.html
corstarsl <- function(x){ 
    require(Hmisc) 
    x <- as.matrix(x) 
    R <- rcorr(x)$r 
    p <- rcorr(x)$P 
    
    ## define notions for significance levels; spacing is important.
    mystars <- ifelse(p < .001, "***", ifelse(p < .01, "** ", ifelse(p < .05, "* ", " ")))
    
    ## trunctuate the matrix that holds the correlations to two decimal
    R <- format(round(cbind(rep(-1.11, ncol(x)), R), 2))[,-1] 
    
    ## build a new matrix that includes the correlations with their apropriate stars 
    Rnew <- matrix(paste(R, mystars, sep=""), ncol=ncol(x)) 
    diag(Rnew) <- paste(diag(R), " ", sep="") 
    rownames(Rnew) <- colnames(x) 
    colnames(Rnew) <- paste(colnames(x), "", sep="") 
    
    ## remove upper triangle
    Rnew <- as.matrix(Rnew)
    Rnew[upper.tri(Rnew, diag = TRUE)] <- ""
    Rnew <- as.data.frame(Rnew) 
    
    ## remove last column and return the matrix (which is now a data frame)
    Rnew <- cbind(Rnew[1:length(Rnew)-1])
    return(Rnew) 
}


```

data$Age
```{r warning=FALSE, message=FALSE, fig.height=3}
par(mfrow=c(1,2)) 
combineSummaryFrame(data[data$System=='C',]$Age, data[data$System=='S',]$Age, rowNames = c('C', 'S'))
invisible(drawHist(data[data$System=='C',]$Age, br=20, main='C')) #suppress ## NULL
invisible(drawHist(data[data$System=='S',]$Age, br=20, main='S'))
```


data$Sex
```{r warning=FALSE, message=FALSE, fig.height=3}
par(mfrow=c(1,2)) 
colnames <- c("men", "women")
combineSummaryFrame(data[data$System=='C',]$Sex, data[data$System=='S',]$Sex, colnames = colnames, rowNames = c('C', 'S'))
invisible(drawPieChart(table(data[data$System=='C',]$Sex), colnames, main='C'))
invisible(drawPieChart(table(data[data$System=='S',]$Sex), colnames, main='S'))
```




data$Comp_Use_Freq
```{r warning=FALSE, message=FALSE, fig.height=3}
par(mfrow=c(1,2)) 
colnames <- c("2-5 hours", "5 hours", "less than one time", "less than 2 hours")
combineSummaryFrame(data[data$System=='C',]$Comp_Use_Freq, data[data$System=='S',]$Comp_Use_Freq, colnames = colnames, rowNames = c('C', 'S'))
invisible(drawPieChart(table(data[data$System=='C',]$Comp_Use_Freq), colnames, main='C'))
invisible(drawPieChart(table(data[data$System=='S',]$Comp_Use_Freq), colnames, main='S'))
```


data$Comp_Use_Know
```{r warning=FALSE, message=FALSE, fig.height=3}
par(mfrow=c(1,2)) 
colnames <- c("beginner", "intermediate", "advanced",  "expert")
combineSummaryFrame(data[data$System=='C',]$Comp_Use_Know, data[data$System=='S',]$Comp_Use_Know, colnames = colnames, rowNames = c('C', 'S'))
invisible(drawPieChart(table(data[data$System=='C',]$Comp_Use_Know), colnames, main='C'))
invisible(drawPieChart(table(data[data$System=='S',]$Comp_Use_Know), colnames, main='S'))
```


data$Selected_Software
```{r warning=FALSE, message=FALSE, fig.height=3.5}
par(mfrow=c(1,2)) 
combineSummaryFrame(data[data$System=='C',]$Selected_Software, data[data$System=='S',]$Selected_Software, rowNames = c('C', 'S'))
invisible(barplot(table(data[data$System=='C',]$Selected_Software), las=2, col = 'red', main='C'))
invisible(barplot(table(data[data$System=='S',]$Selected_Software), las=2, col = 'red', main='S'))
```



Part 2.2

```{r warning=FALSE, message=FALSE}

data_filtered <- data[data$System == 'C' & data$Age  >= 18 & data$Age<=49,]

stat_data <- data_filtered[ ,names(data_filtered) %in% c("clarity", "politeness", "satisfaction")]
stat_res <- data.frame(
  apply(stat_data, 2, length), 
  apply(stat_data, 2, mean, na.rm=TRUE), 
  apply(stat_data, 2, sd, na.rm=TRUE), 
  apply(stat_data, 2, min, na.rm=TRUE), 
  apply(stat_data, 2, max, na.rm=TRUE), 
  apply(stat_data, 2, kurtosis, na.rm=TRUE),
  apply(stat_data, 2, skewness, na.rm=TRUE)
)
colnames(stat_res) <- c('count', 'mean', 'sd', 'min', 'max', 'kurtosis', 'skewness')
stat_res
```


#Part 2.3

```{r warning=FALSE, message=FALSE}
stat_data_2.3 <- data_filtered[ ,names(data_filtered) %in% c("Age", "clarity", "politeness", "satisfaction")]
corstarsl(stat_data_2.3)
```


#Part 2.4
```{r warning=FALSE, message=FALSE}

lmodel1 = lm(satisfaction ~ Age+Sex, data = data_filtered)
summary(lmodel1)

lmodel2 = lm(satisfaction ~ Age+Sex+clarity+politeness, data = data_filtered)
summary(lmodel2)

anova(lmodel1, lmodel2)

```